---
title: "Bey2ollak Data Analysis Project"
output: html_document
---
```{r}
library(ggplot2)
library(dplyr)
```

# Data Processing:

```{r}
  file <- "~/Downloads/all-semi-unique.csv"
  all_data <- read.csv(file, encoding="UTF-8")
```

# Data Cleaning & Preparation:


```{r}
factor(all_data$ad.lid)

keep <- c("crawl_date", "rd.nm", "rd.ri", "rd.stid", "rd.hr", "rd.mn", "rd.new", "rd.strq", "rd.cmrq", "rd.rp.nm", "rd.rp.hr", "rd.rp.mn", "rd.rp.stid", "rd.rp.cm", "rd.rp.cmid")
cut_data <- all_data[keep]
head(cut_data)

cut_data %>% filter(rd.rp.cm == "mashy")
cut_data %>% filter(rd.rp.cm == "lazeez")


unique(cut_data$rd.rp.cmid) %>% length()

unique_data = cut_data %>% filter(!duplicated(cut_data$rd.rp.cmid))
View(unique_data)

ggplot(unique_data) + geom_bar(aes(x=rd.stid))
ggplot(unique_data) + geom_bar(aes(x=rd.stid,y= rd.new), stat="identity") 

```

## Time Formats and columns:
```{r}
  unique_data$date_time_formatted = strptime(unique_data$crawl_date, "%a %b %d %H:%M:%S UTC %Y", tz="UTC")
unique_data$date_time_formatted = unique_data$date_time_formatted - (unique_data$rd.rp.hr*60*60 + unique_data$rd.rp.mn*60)
```

## Cairo Time:
```{r}
  unique_data$date_time_formatted = unique_data$date_time_formatted + 2*60*60
  unique_data$report_hour = as.numeric(unique_data$date_time_formatted %>% format("%H"))
  unique_data$report_min = as.numeric(unique_data$date_time_formatted %>% format("%M"))
```

# Plotting & Comprehension:
```{r}
ggplot(unique_data) + geom_point(aes(x=rd.stid,y= report_hour), stat="identity")

ggplot() + geom_histogram(data = unique_data, aes(x=report_hour))

ggplot() + geom_histogram(data = unique_data, aes(x=rd.stid))

ggplot(unique_data)+geom_point(aes(unique_data$report_hour, unique_data$rd.stid, color=factor(unique_data$rd.stid)))

 makram <- unique_data %>% filter(rd.ri==678)
ggplot(makram,aes(y = makram$rd.stid, x = makram$report_hour)) + geom_point()
unique_data$report_day =  weekdays((unique_data$date_time_formatted))
ggplot(unique_data,aes(y = rd.stid, x = report_day)) + geom_point()


```


##Frequency of reports across weekdays:
```{r}
days_grouped <- data.frame(table(unique_data$report_day))
ggplot(days_grouped,aes(y = Freq, x = Var1)) + geom_point()
```

##Hypothesis: Frequency of Specific Congestion Reports are correlated with the total number of reports across time

The behaviour of the frequency of high congestion reports(with status ID of 4 or 5), low congestion reports(with status ID of 1 or 2) and question reports(with status ID of 10) across time

Frequency of reports across weekdays:
```{r}
hours_grouped <- data.frame(table(unique_data$report_hour))
ggplot(hours_grouped,aes(y = Freq, x = Var1)) + geom_point()

congested_data <- unique_data %>% filter(rd.rp.stid >=4 & rd.rp.stid <= 5)
hours_grouped_congested <- data.frame(table(congested_data$report_hour))

ggplot() + geom_point(data = hours_grouped,aes(y = Freq, x = Var1)) + geom_point(data = hours_grouped_congested,aes(y = Freq, x = Var1), color = "red")

questions_data <- unique_data %>% filtecor(rd.rp.stid ==10)
hours_grouped_questions <- data.frame(table(questions_data$report_hour))

ggplot() + geom_point(data = hours_grouped,aes(y = Freq, x = Var1)) + geom_point(data = hours_grouped_questions,aes(y = Freq, x = Var1), color = "red")

clear_data <- unique_data %>% filter(rd.rp.stid >=1 & rd.rp.stid <= 2)
hours_grouped_clear <- data.frame(table(clear_data$report_hour))

ggplot() + geom_point(data = hours_grouped,aes(y = Freq, x = Var1)) + geom_point(data = hours_grouped_congested,aes(y = Freq, x = Var1), color = "red") + geom_point(data = hours_grouped_clear ,aes(y = Freq, x = Var1), color = "green") + geom_point(data = hours_grouped_questions,aes(y = Freq, x = Var1), color = "blue")

cor(hours_grouped$Freq,hours_grouped_congested$Freq)
cor(hours_grouped$Freq,hours_grouped_clear$Freq)
cor(hours_grouped$Freq,hours_grouped_questions$Freq)

```
- The first hours of the day usually has more question type reports than the other types.
- Rush hours increases congestion reports of status ids 1,2,4,5
- za7ma & mafeesh amal are more likely to be reported from 5 to 7 pm

##Hypothesis: Studying user behaviour to look for abnormalities
- An example of that is when the status id of a road is 1 and a user adds a report with a status id of 5.
- This might indicate that the user is giving a dishonest report or not.
- However detecting this behaviour more than once across 2 weeks for a certain user makes it useful to review his reports to avoid misbehaved users.
```{r}
extreme_reports <- unique_data %>% filter(rd.stid <= 5 & rd.rp.stid <=5 & abs(rd.rp.stid - rd.stid) == 4)

factor(extreme_reports$rd.rp.nm)
extreme_users <- data.frame(table(extreme_reports$rd.rp.nm))

extreme_users <- data.frame(table(extreme_reports$rd.rp.nm)) %>% filter(Freq > 2)
View(extreme_users)
```

- extreme users tables has the reporters who have given an extreme report more than 2 times.
- The fact that bey2ollak GPS has the most of those extreme reports is good because it's a secure channel.
- Fa3el Kheir is the second contributor which suggests the need for a way to verify the integrity of data coming from anonymous accounts
- 2 users have given 6 extreme reports accross 2 weeks.





salah_salem1_data <- unique_data %>% filter(rd.ri == 686 & rd.rp.stid >=4 & rd.rp.stid <= 5)
salah_salem2_data <- unique_data %>% filter(rd.ri == 687 & rd.rp.stid >=4 & rd.rp.stid <= 5)
salah_salem1 <- data.frame(table(salah_salem1_data$report_hour))
salah_salem2 <- data.frame(table(salah_salem2_data$report_hour))
ggplot() + geom_point(data = salah_salem1,aes(y = Freq, x = Var1)) + geom_point(data = salah_salem2,aes(y = Freq, x = Var1), color = "red")

